\textls[-0]{\thetitle}

### 2023-03-05 canonicitymodel.tex
Save. Working on Appendices.

Like most logical relation proof,  we interpret each judgement and prove compatibility lemma.

>>>>

Like most logical relation proof,  we interpret each judgement, inductively interpret each syntax piece and prove compatibility lemma.

\begin{align*}
  \denotesC{\goodCtx{\Gm}{i}} & \text{ is a Set of closed substitution} \goodSub{\cdot}{\_}{\Gm} \\
  &\text{we define } \goodCtxS{\Gm}{i} :\iff \denotesS{\goodCtx{\Gm}{i}} \text{ is defined} \\
  \denotesC{\goodType{\Gm}{T}{}} & \text{ is a function maps to Set s.t.} \\
  & \text{for arbitrary } \gm \in \denotesC{\goodCtx{\Gm}{}}, \denotesC{\goodType{\Gm}{T}{}}(\gm) \text{ is a Set of closed terms } \goodTerm{\cdot}{\_}{\sub{T}{\gm}} \\ 
  &\text{we define } \goodTypeS{\Gm}{T}{i} : \iff \denotesS{\goodType{\Gm}{T}{i}} \text{ is defined }
\end{align*}

Now that we construct the above model, we can map an arbitrary closed term $\goodTerm{\cdot}{t}{\cB}$ to get the result

Then we extend the above model to \TT .
